Adopting agile in the large: motivations, success factors and challenges

### 2014-01-09 journal/article.tex
Inductive coding description

Based on the research questions and intended focus of the research, we defined
three facets to guide any inclusion/exclusion decisions: agile software
engineering, focus on transformation, and large scale. The first facet
covers primary studies focusing on software engineering organizations applying
or striving to apply agile methods. The second facet states that included
studies must provide insights relevant to organizational transformation, and
specifically to the research questions. The third facet underlines the
particular contribution we aim to provide with this research, namely the
exclusive focus on large organizations. These three facets were used for
inclusion and exclusion in each study selection step, including search string
design, filtering by abstracts, and full text filtering.

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. As a result we excluded the facet
\emph{large scale} from the keyword search, and relied on manual filtering.
Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we considered only articles including the term ``software'' or
articles published in relevant conferences. Instead of further engineering the
search terms, which proved to result in excluding some relevant articles, we
chose to manually filter the remaining search results. The resulting facets and
keywords are listed in Table \ref{table:searchterms}.

@@

-- How to choose a code?

-- Any statement that represents its own concept is coded. The statement becomes
   a quote.

-- The statements that are quoted must related to the research questions, or
   contextual codes.

-- The concept and quote is first considered as free standing, i.e. not
   related to any existing code.

-- If there is an existing code that is close to the new code it is considered
   to use the existing code.

-- If the primary source makes an indirect statement relating to a code?

%% -----------

-- Considering that mentioning the inclusion of a factor as a success, then
   would the absence of the same factor be a challenge?

-- If a challenge is described also try to include the resolution in the
   quotation, if one is available. This should broaded the understanding of the
   challenges when looking at the quotations only.

>>>>

Based on the research questions and intended focus of the research, we defined
three facets to guide inclusion/exclusion decisions: agile software engineering,
focus on transformation, and large scale. The first facet covers primary studies
focusing on software engineering organizations applying or striving to apply
agile methods. The second facet states that included studies must provide
insights relevant to organizational transformation, and specifically to the
research questions. The third facet underlines the particular contribution we
aim to provide with this research, namely the exclusive focus on large
organizations. These three facets were used for inclusion and exclusion in each
study selection step, including search string design, filtering by abstracts,
and full text filtering.

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. Therefore we decided to exclude the
facet \emph{large scale} from the keyword search, with the consequence of
increasing the manual filtering effort in the subsequent steps.
Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we included only articles including the term ``software'' or
articles published in relevant conferences. Instead of engineering the search
terms any further, which proved to result in excluding some relevant articles,
we chose to rely more on manual filtering. The resulting facets and keywords are
listed in Table \ref{table:searchterms}.

@@

The inductive coding was done according to the guidelines described below.

A passage of text that presents any concept relating to the research questions
or the contextual codes becomes a quotation. If the quotation corresponds
closely to a concept that has already been coded the existing code is used.
Otherwise a new code is created, and the code is assigned to one of the
predefined code families. The labels of existing codes may need to be adjusted
when new quotations are assigned. Many codes may be assigned to one quotation
and quotations of different codes may be overlapping.

The length of the text passage that make up a quotation may vary. For the
contextual codes the quoted passage should be of minimal length. For other
quotes the length of the quotation should be long enough to highlight the
context of the concept the quotation, varying from a few sentences to one
paragraph, or even several paragraphs. As an example of context of the
quotation, if a transformation challenge is described by a quotation it would be
good if also the source or resolution of the challenge could be included in the
quoted text passage. Having enough context should broaden the understanding
of the coded concept when looking at the quotation in isolation..

% -- Considering that mentioning the inclusion of a factor as a success, then
%    would the absence of the same factor be a challenge?
